Modeling Macroeconomic Phenomena \\with Multi-Agent Reinforcement Learning

### 2019-12-06 paper/paper.tex

\subsubsection{Q Actor-Critic}
An alternative family of policy gradient methods is the \textit{actor-critic} family. In these algorithms, the actor component computes the log probabilities $\log \pi_{\theta}(s, a)$ while the critic component approximates the function $Q(s, a)$. We considered this set of algorithms because it carries the convergence advantages of general policy gradient methods while also approximating Q-values with higher sample efficiency. As with REINFORCE, we again used neural networks with one hidden layer for both the actor and critic. 
\begin{algorithm}
\caption{Q Actor Critic}\label{euclid}
\begin{algorithmic}[1]
\Procedure{Actor\_Critic}{}
\State $\text{Initialize policy and Q-network parameters }\theta, \omega$
\For {$i = 1, 2, \ldots, M$}
\State $\text{Initialize state and action }s_1, a_1 \sim \pi_{\theta}(a|s_1)$.
\For {$t = 1, 2, \ldots, T-1$}
\State Record reward $r_t$ and next state $s_{t+1}$
\State Sample the next action $a_{t+1} \sim \log \pi_{\theta}(a|s_{t+1})$
\State $\text{Update } \theta \leftarrow \theta + \alpha_{\theta} Q_{\omega}(s_t,a_t) \nabla_{\theta} \pi_{\theta} (s_t, a_t)$
\State $\text{Compute temporal difference error: }\delta_t = r_t + \gamma Q_{\omega}(s_{t+1}, a_{t+1}) - Q_{\omega}(s_{t}, a_{t})$
\State $\text{Update } \omega \leftarrow \omega + \alpha_{\omega} \delta_t \nabla_{\omega} Q_{\omega} (s_t, a_t)$
\EndFor
\EndFor
\State \Return {$\theta, \omega$}
\EndProcedure
\end{algorithmic}
\end{algorithm}
In the current version we have implemented, the

[************** Q-network doesn't converge, maybe because we have an unstable target, requiring a target network]

@@

>>>>

\subsubsection{Actor-Critic}
An alternative family of policy gradient methods is the \textit{actor-critic} family. In these algorithms, the actor component computes the log probabilities $\log \pi_{\theta}(s, a)$ while the critic component approximates the performance of the action. We considered this set of algorithms because in theory, it carries the convergence advantages of general policy gradient methods while also approximating Q-values with higher sample efficiency. In this scenario, we tested Q Actor-Critic, in which the critic computes the Q-values $Q(s,a)$, as well as Advantage Actor-Critic (A2C), in which the critic computes the advantage $Q(s, a) - V(s)$; the idea of using the advantage vs the $Q$-value is to compare the quality of the action with a stable baseline, reducing variance.  As with REINFORCE, we again used neural networks with one hidden layer for both the actor and critic. Note also that we get to update the parameters after every action via TD learning.
\begin{algorithm}
\caption{Q Actor Critic}\label{euclid}
\begin{algorithmic}[1]
\Procedure{Actor\_Critic}{}
\State $\text{Initialize policy and Q-network parameters }\theta, \omega$
\For {$i = 1, 2, \ldots, M$}
\State $\text{Initialize state and action }s_1, a_1 \sim \pi_{\theta}(a|s_1)$.
\For {$t = 1, 2, \ldots, T-1$}
\State Record reward $r_t$ and next state $s_{t+1}$
\State Sample the next action $a_{t+1} \sim \log \pi_{\theta}(a|s_{t+1})$
\State $\text{Update } \theta \leftarrow \theta + \alpha_{\theta} Q_{\omega}(s_t,a_t) \nabla_{\theta} \pi_{\theta} (s_t, a_t)$
\State $\text{Compute temporal difference error: }\delta_t = r_t + \gamma Q_{\omega}(s_{t+1}, a_{t+1}) - Q_{\omega}(s_{t}, a_{t})$
\State $\text{Update } \omega \leftarrow \omega + \alpha_{\omega} \delta_t \nabla_{\omega} Q_{\omega} (s_t, a_t)$
\EndFor
\EndFor
\State \Return {$\theta, \omega$}
\EndProcedure
\end{algorithmic}
\end{algorithm}

@@

\begin{figure}[h]
\begin{tikzpicture}[every mark/.append style={mark size=1pt}]
  \begin{axis}[
    xlabel=Episode,
    ylabel=Policy Loss,
    legend style={at={(1,0)}, anchor=south east}
  ]
  \addplot table [y=pl, x=i]{a2c.dat};
  \addlegendentry{Firm}
  \end{axis}
\end{tikzpicture}
\caption{Policy Network Loss in Actor Critic Method}
\label{plt:a2cpolicyloss}
\end{figure}

\begin{figure}[h]
\begin{tikzpicture}[every mark/.append style={mark size=1pt}]
  \begin{axis}[
    xlabel=Episode,
    ylabel=Critic Loss,
    legend style={at={(1,0)}, anchor=south east}
  ]
  \addplot table [y=al, x=i]{a2c.dat};
  \addlegendentry{Firm}
  \end{axis}
\end{tikzpicture}
\caption{Critic Network Loss in Actor Critic Method}
\label{plt:a2cadvloss}
\end{figure}
